\documentclass[]{exam}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{subcaption}

\pagestyle{empty}

\begin{document}
  \begin{center}
    \fbox{\fbox{\parbox{5.5in}{\centering Answer the questions in the spaces
    provided on the question sheets. If you run out of room for an answer,
    continue on a separate sheet of paper.}}}
  \end{center}

  \section*{Conditional probability}

  \begin{questions}
    \question Suppose that we flip a coin three times, and all eight
      possibilities are equally likely. Moreover, suppose we know that the event
      $F$, that the first flip comes up tails, occurs. Given this information,
      what is the probability of the event $E$, that an odd number of tails
      appears?
      \begin{solution}
        Because the first fip comes up tails, there are only four possible
        outcomes: $TTT, TTH, THT,$ and $THH$, where $H$ and $H$ represent heads
        and tails, respectively. An odd number of tails appears only for the
        outcomes $TTT$ and $THH$. Because the eight outcomes have equal
        probability, each of the four possible outcomes, given that $G$ occurs,
        should also have an equal probability of $1/4$. This suggests that we
        should assign the probability of $2/4=1/2$ to $E$, given that $F$
        occurs.

        $p(E|F)=\frac{p(E \cap F)}{p(F)}=\frac{\frac{2}{8}}{\frac{4}{8}}=\frac{1}{2}$
      \end{solution}
      \vspace{\stretch{1}}

    \question Are events $E$ and $F$ independent?
      \begin{solution}
        $p(E \cap F)=\frac{2}{8}=\frac{4}{8}\cdot\frac{4}{8}=p(E)\cdot p(F)$
      \end{solution}
      \vspace{\stretch{1}}

    \question Exercise 9.3.1 from zyBooks

    \question Exercise 9.3.6 from zyBooks
  \end{questions}
\end{document}
