\documentclass[]{exam}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{subcaption}

\pagestyle{empty}

\begin{document}
  \begin{center}
    \fbox{\fbox{\parbox{5.5in}{\centering Answer the questions in the spaces
    provided on the question sheets. If you run out of room for an answer,
    continue on a separate sheet of paper.}}}
  \end{center}

  \section*{Bayes' theorem}

  \begin{questions}
    \question Suppose we have two coins. The first coin is a fair coin and the
      second coin is biased. The biased coin comes up heads with probability .75
      and tails with probability .25. We select a coin at random and flip the
      coin ten times. The results of the coin flips are mutually independent.
      The result of the 10 flips is: T,T,H,T,H,T,T,T,H,T. What is the
      probability that we selected the biased coin?
      \begin{solution}
        Let $B$ be the event that we selected the biased coin.
        $p(B)=p(\overline{B})=1/2$.

        Let $Y$ be the event that the outcomes is T,T,H,T,H,T,T,T,H,T. Because
        the results of the flips are independent, $p(Y|\overline{B}) =
        (1/2)^{10}$. Also $p(Y|B) = (1/4)^7(3/4)^3$. Using Bayes' Theorem:

        $p(B|Y)=\dfrac{p(Y|B)p(B)}{p(Y|B)p(B)+p(Y|\overline{B})p(\overline{B})}
        =\dfrac{(1/4)^7(3/4)^3(1/2)}{(1/4)^7(3/4)^3(1/2)+(1/2)^{10}(1/2)} =
        \dfrac{27}{27+2^{10}}\approx 0.0257$.
      \end{solution}
      \vspace{\stretch{1}}

    \question Na\"{i}ve Bayes classifier

      \begin{parts}
        \part Using Bayes' theorem, compute the probability that a traveler
          survived (\emph{column D}) given their ticket class (\emph{column A}).
          \begin{solution}
            $p(0|ticket)=\dfrac{p(ticket|0)*p(0)}{p(ticket)}$.

            $p(1|ticket)=\dfrac{p(ticket|1)*p(1)}{p(ticket)}$.
          \end{solution}
          \vspace{\stretch{1}}

        \part Given an unknown traveler, make a prediction, using results from
          Part (a) about whether or not they will survive based on their ticket
          class.
          \vspace{\stretch{1}}

          \begin{subparts}
            \subpart What do you notice about this predictive model? How can we
              improve it?
              \vspace{\stretch{1}}
          \end{subparts}

        \part Improve model.
          \vspace{\stretch{1}}
      \end{parts}
  \end{questions}
\end{document}
